\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-04-02 manuscript/manuscript.tex
opening paragraph

\title{\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for
  Marginal Distributions of Stationary Time Series}
\if0\blind
{
  \author{Mathew Chandy, %\\
%   \href{mailto:mathew.chandy@uconn.edu}
%   {\nolinkurl{mathew.chandy@uconn.edu}}\\
  Elizabeth Schifano\\
  Jun Yan, %\\
  Xianyang Zhang\\
} \fi

@@

The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ be that $X_i$'s follow the
hypothesized distribution~$F$.
If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function, the KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}
As sample size $n\to \infty$, the distribution of $T_n$ converges to that of the
absolute value of standard Brownian bridge, which is known as the Kolmogorov
distribution \citep{stephens1974edf}. The distribution function can be
accurately evaluated in modern statistical software
\citep{marsaglia2003evaluating}. The KS test can be applied to a variety of
fields. Examples are cosmic microwave background 
radiation \citep{naess2012application},
count rate of radioactive data \citep{aslam2020introducing},
gear condition monitoring \citep{andrade2001gear},
images of breast cancer tumors \citep{demidenko2004kolmogorov},
and financial markets \citep{lux2001turbulence}.

@@

\jy{This reference is an example of abuse in time series settings:
Tuncer, O., Ates, E., Zhang, Y., Turk, A., Brandt, J., Leung, V. J., Egele, M., and Coskun, A. K. (2019), “Online Diagnosis of Performance Variation in HPC Systems Using Machine Learning,” IEEE Transactions on Parallel and Distributed Systems, 30, 883–896.
}
\mc{addressed}

>>>>

\title{\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for
  Marginal Distributions of Stationary Time Series}
\if0\blind
{
  \author{Mathew Chandy, %\\
%   \href{mailto:mathew.chandy@uconn.edu}
%   {\nolinkurl{mathew.chandy@uconn.edu}}\\
  Elizabeth Schifano\\
  Jun Yan\\
  Xianyang Zhang\\
} \fi

@@

The standard one-sample Kolmogorov-Smirnov (KS) test is widely
recoganized as effective good-of-fit test for continuous distributions.
Consider $X_1, ..., X_n$, a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ that $X_i$'s follow a specific
hypothesized distribution~$F$.
If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function, the KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}
As sample size $n\to \infty$, the distribution of $T_n$ converges to that of the
absolute value of standard Brownian bridge, which is known as the Kolmogorov
distribution \citep{stephens1974edf}. This distribution function is
precisely computable using contemporary statistical software
\citep{marsaglia2003evaluating}. The versatility of the KS test allows its
application across various domains, such as analyzing cosmic microwave
background radiation \citep{naess2012application}, monitoring the count rate of
radioactive data \citep{aslam2020introducing}, gear condition monitoring
\citep{andrade2001gear}, studying images of breast cancer tumors
\citep{demidenko2004kolmogorov}, and examining financial markets
\citep{lux2001turbulence}.

@@
